
My first R markdown file 
============================

This is my first R markdown file.

Here, we're load some data.

```{r}
library(datasets)
data("airquality")
summary(airquality)
```

Let's first made a pairs plot of data.

```{r}
pairs(airquality)
```

Here's a regression model of ozone on wind, solar radiation, and temperature.

```{r}
library(stats)
fit <- lm(Ozone~Wind+Solar.R+Temp, data=airquality)
summary(fit)
```

Here's on unordered list:

* First element 

* Second element


here is a code chunk

```{r}
set.seed(1)
x <- rnorm(100)
mean(x)
```


```{r, echo=FALSE}
set.seed(1)
x <- runif(100)
mean(x)
```


Let's  simulate some data.
```{r simulatedata, echo=F}
x <- rnorm(100)
y <- x+rnorm(100, sd=0.5)
```
Here is a scatterplot of the data

```{r scatterplot, fig.height=6}
par(mar=c(5,4,1,1), las=1)
plot(x, y, main="My simulated data")
```


# Make table with xtable

## introduction 

```{r fitmodel}
fit <- lm(Ozone~Wind+Temp+Solar.R, data=airquality)
```

Here is a table of regression coefficients

```{r showtable, results="asis"}
library(xtable)
xt <- xtable(summary(fit), align=c("c", "c", "c", "c", "c"))
print(xt, type="html")
```



what if one cunk takes a long time to run?
All chunks have to be re-computed every time you re-knit the file
the cache=T option can be set on a chunk-by-chunk basis to store results of computation

If the data or code changes, you need to re-run the cached code chunks 
```{r showtable1, results="asis", cache=T}
library(xtable)
xt <- xtable(summary(fit), align=c("c", "c", "c", "c", "c"))
print(xt, type="html")
```
