---
title: "Reproducible Research Course Project Week2"
author: "Sang Don"
date: "2019년 6월 20일"
output: html_document
---

# reproducible research coursera project 

first, I created the data file. Then I unziped the activity monitoring data file and load the activity data using the read.csv function. 

```{r read the data, echo=TRUE}
if (!file.exists("data")) {
        dir.create("data")
}

Url <- "https://d396qusza40orc.cloudfront.net/repdata%2Fdata%2Factivity.zip"
download.file(Url, destfile = "./data/monitoringdata.zip", method = "curl")
unzip( "./data/monitoringdata.zip", exdir = "./data")

act <- read.csv("./data/activity.csv")
DT::datatable(act)
```


## What is mean total number of steps taken per day?

1. I calculated the total number of steps taken per day

```{r sum, echo=TRUE}
act %>% group_by(date) %>%
        summarize(sumsteps=sum(steps, na.rm = T))
```


2. I maked a histogram of the total number of steps taken each day

```{r histogram, echo=TRUE}
library(tidyverse)
act %>% group_by(date) %>%
        summarize(sumsteps=sum(steps, na.rm = T)) %>% 
        ggplot(aes(x=sumsteps))+geom_histogram(bins = 30)+theme_bw()
```


3. I caculated and reported the mean and median of the total number of steps taken per day

```{r mean, echo=TRUE}
library(knitr)
act %>% group_by(date) %>%
        summarize(sumsteps=sum(steps, na.rm = T)) %>% 
        summarize(mean=mean(sumsteps, na.rm = T), median=median(sumsteps, na.rm = T))
```


## What is the average daily activity pattern?


I maked a time series plot of the 5-minute interval (x-axis) and the average number of steps taken, averaged across all days (y-axis)
```{r timeseries plot, echo=TRUE}
glimpse(act)
act$date <- lubridate::ymd(act$date)
act %>% group_by(interval) %>% 
        summarize(mean=mean(steps, na.rm=TRUE)) %>% 
        ggplot(aes(x=interval, y=mean))+
        geom_line(size=1)+
        theme_bw()
```


Which 5-minute interval, on average across all the days in the dataset, contains the maximum number of steps?

```{r maximum of steps, echo=TRUE}
act %>% group_by(interval) %>% 
        summarize(intervalmean=mean(steps, na.rm = TRUE)) %>% 
        filter(intervalmean==max(intervalmean))
```



## Imputing missing values


there are 2304 missing value in activity dataset

```{r count NA, echo=TRUE}
sum(is.na(act))
```


I devised a strategy for filling in all of the missing values in the dataset. I selected the method of mean imputation because missing value exist only steps variable    

```{r NA strategy, echo=TRUE}
na.count=apply(act, 2, function(x) sum(is.na(x)))
na.count

library(VIM)
aggr(act, prop=FALSE, numbers=TRUE)

mean(act$steps, na.rm = T)
act$steps <- ifelse(is.na(act$steps), 37.3826, act$steps)
table(is.na(act$steps))
```


I maked a histogram of the total number of steps taken each day and Calculate and report the mean and median total number of steps taken per day. 

```{r histogram and summarize, echo=TRUE}
act %>% group_by(date) %>% 
        summarize(stepsday=sum(steps)) %>% 
        ggplot(aes(x=stepsday))+geom_histogram(bins = 30)+
        theme_bw()

act %>% group_by(date) %>% 
        summarize(stepsday=sum(steps)) %>% 
        summarize(mean=mean(stepsday), median=median(stepsday))
```



## Are there differences in activity patterns between weekdays and weekends?


1. I created a new factor variable in the dataset with two levels – “weekday” and “weekend” indicating whether a given date is a weekday or weekend day.

```{r weekdays and weekends, echo=TRUE}
head(weekdays(act$date))
act <- act %>% mutate(week=ifelse(weekdays(date)%in%c("Monday", "Tuesday", "Wednesday", "Thursday", "Friday"), "weekend", "weekday"))
table(act$week)

```


2. I maked a panel plot containing a time series plot of the 5-minute interval (x-axis) and the average number of steps taken, averaged across all weekday days or weekend days (y-axis). 

```{r panel plot, echo=TRUE}
act %>% group_by(week, interval) %>% 
        summarize(mean=mean(steps, na.rm=TRUE)) %>% 
        ggplot(aes(x=interval, y=mean, color=week))+
        geom_line(size=1)+
        facet_wrap(~week, ncol=1, nrow = 2)+
        theme_bw()
```