---
title: "reproducible research assignment 2"
author: "Sang Don"
date: "2019년 6월 22일"
output: html_document
---

# NOAA storm data analysis 


## Question 

1. Across the United States, which types of events are most harmful with respect to population health?
2. Across the United States, which types of events have the greatest economic consequences?

## load the package
```{r package}
library(DT)
library(R.utils)
library(tidyverse)
```


## load the data

```{r load data}
fileUrl <- "https://d396qusza40orc.cloudfront.net/repdata%2Fdata%2FStormData.csv.bz2"
download.file(fileUrl, destfile =  "./reproducible research/data/FStormData.csv.bz2")
stormdata <- fread("./reproducible research/data/FStormData.csv.bz2")
```

```{r data processing}
glimpse(stormdata)
table(is.na(stormdata))

apply(stormdata, 2, function(x) sum(is.na(x)))
```


## Variable description

* STATE__ : 
* BGN_DATE
* BGN_TIME
* TIME_ZONE
* COUNTY
* COUNTYNAME
* STATE      
* EVTYPE
* BGN_RANGE
* BGN_AZI
* BGN_LOCATI
* END_DATE
* END_TIME
* COUNTY_END
* COUNTYENDN
* END_RANGE
* END_AZI
* END_LOCATI
* LENGTH
* WIDTH
* F
* MAG
* FATALITIES
* INJURIES
* PROPDMG
* PROPDMGEXP
* CROPDMG
* CROPDMGEXP
* WFO
* STATEOFFIC
* ZONENAMES
* LATITUDE
* LONGITUDE
* LATITUDE_E
* LONGITUDE_ 
* REMARKS
* REFNUM    
> 




